High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-10-16 Draft_V4046Sgr_mnras.tex
Update Draft_V4046Sgr_mnras.tex

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam: $ 0\farcs04 \, \times \, 0\farcs06$, and the small orange ellipse shows an estimated {\tt uvmem} beam size of: $\sim0\farcs01 \, \times \, \sim0\farcs02$. The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$. For all the images in the figure the colour scale is linear.}
  \label{fig:two}
\end{figure*}

>>>>

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that illustrate the N\_ALC\_YJH\_S coronagraph (inner working angle $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc). Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs04 \, \times \, 0\farcs06$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs01 \, \times \, \sim0\farcs02$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: 1.65\,$\upmu m$ simulated image of the parametric model. Bottom right panel: 1.3\,mm simulated image of the parametric model. The yellow ellipse shows the size of the beam: $0\farcs04 \, \times \, 0\farcs06$. For all the images in the figure the colour scale is linear.}
  \label{fig:two}
\end{figure*}
